---
title: "Homework 1"
author: "Matthew T. Russell"
date: "9/29/2021"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

###### Creating a data frame with 4 columns:
* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r problem_1}
set.seed(12551)

prob_1_df <- tibble(
  rand_norm_10 = rnorm(10),
  greater_than_0 = rand_norm_10 > 0,
  housewives = c("kyle", "kenya", "vicki", "cynthia", "eileen", "dorit", "jeana",
                 "phaedra", "sutton", "garcelle"),
  citrus = factor(c(rep("lemon", 3), rep("lime", 3), rep("orange", 4)))
)

```

```{r problem 1: show the df w/o the code, echo=FALSE}
prob_1_df
```

###### Means of each column:

```{r problem_1: means of each column, warning=FALSE, collapse=TRUE}
mean(pull(prob_1_df, rand_norm_10)) 
mean(pull(prob_1_df, greater_than_0))
mean(pull(prob_1_df, housewives))
mean(pull(prob_1_df, citrus))
```

We are able to take the means of our numeric and logical vectors but not the
character and factor vectors. 

###### Converting columns to numeric:

```{r problem_1: convert to numeric, results='hide', warning=FALSE}
as.numeric(pull(prob_1_df, greater_than_0))
as.numeric(pull(prob_1_df, housewives))
as.numeric(pull(prob_1_df, citrus))
```
The logical vector can be converted to a numeric vector because it's binary: false goes to 0
and true goes to 1. The factor vector can be converted to a numeric vector because each factor is
changed to its corresponding level. Character vectors cannot be converted to a numeric vector because
they do not represent numeric values. It helps explain why we're able to get a mean for the
logical vector since the T/F go to 1/0, so our mean is the number of true values divided by the number of total values. To get the mean for a factor vector, we'd need to convert it to a numeric vector and then take the mean. 

###### Loading 'Penguins' data and data description:

```{r problem_2: load and describe data, collapse=TRUE}
data("penguins", package = "palmerpenguins")
```

This data include the following information about penguins: `r colnames(penguins)`. There are 
`r length(unique(pull(penguins, species)))` species of penguins (`r unique(pull(penguins, species))`)
found on `r length(unique(pull(penguins, island)))` islands (`r unique(pull(penguins, island))`) from
`r min(pull(penguins, year))` to `r max(pull(penguins, year))`.


