---
title: "Homework 1"
author: "Matthew T. Russell"
date: "9/29/2021"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

###### Creating a data frame with 4 columns:
* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r problem_1}
set.seed(12551)

prob_1_df <- tibble(
  rand_norm_10 = rnorm(10),
  greater_than_0 = rand_norm_10 > 0,
  housewives = c("kyle", "kenya", "vicki", "cynthia", "eileen", "dorit", "jeana",
                 "phaedra", "sutton", "garcelle"),
  citrus = factor(c(rep("lemon", 3), rep("lime", 3), rep("orange", 4)))
)

```

```{r problem 1: show the df w/o the code, echo=FALSE}
prob_1_df
```

###### Means of each column:

```{r problem_1: means of each column, warning=FALSE, collapse=TRUE}
mean(pull(prob_1_df, rand_norm_10)) 
mean(pull(prob_1_df, greater_than_0))
mean(pull(prob_1_df, housewives))
mean(pull(prob_1_df, citrus))
```

We are able to take the means of our numeric and logical vectors but not the
character and factor vectors. 


